### 2021-07-08 rad-icfp-2021/generalization.tex
minor
added a paragraph 7.2

@@

This time, there is a linear usage of the continuation variable !Y! (and of the variables !x1,$\ldots$xn! too).

We note that adding conditionals does not break differentiability as long as there are no non-trivial primitives $\reals\to\BB$.
Non smooth functions such as the Rectified Linear Unit (ReLU) in machine learning which can be defined as $ReLU(x)\defeq max(0,x)$ 
requires a non smooth primitive such as $>0: \reals\to\BB$. In several AD systems such as TensorFlow, 
the condition is evaluated before differentiation is applied, and so conditionals are never directly differentiated.

>>>>

\smartpara{Recipe for adding array operators} To add more array operators to our language, 
one doesn't need to go through UNF and most of the backend of our work can be used as a black box.
The non-smooth variables of the operator (typically booleans or integers) should be considered as external the language, similarly to the way we treat the index $n$ of arrays.
If the operator has type $A\to B$, then one should provide its transpose Jacobian, a term $B\to A$. 
Such operators can often be unrolled to first-order programs. To check correctness of the given Jacobian, it suffices to 
check that the semantics of the transpose Jacobian matches the Jacobian of the unrolled program. 
To ensure the complexity guarantee of the whole transformation, one needs to check that there a linear usage of the continuation variable $Y$ and that the cost of the 
proposed Jacobian is at most $k$ times the complexity of the operator.

@@

This time, there is a linear usage of the continuation variable !Y!. We note that adding conditionals does not break differentiability as long as there are no non-trivial primitives $\reals\to\BB$.
Non smooth functions such as the Rectified Linear Unit (ReLU) in machine learning which can be defined as $ReLU(x)\defeq max(0,x)$ 
requires a non smooth primitive such as $>0: \reals\to\BB$. In several AD systems such as TensorFlow, 
the condition is evaluated before differentiation is applied, and so conditionals are never directly differentiated.
